The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2025-04-25 Restud submission/donde_restud-FIRST-DRAFT.tex
First set of edits after R&R

\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

Financial institutions often restrict choice using built-in commitment mechanisms like fixed repayment streams. These widely used attributes are meant to lower default and increase lender profit. At the same time, these firms often shroud those features by embedding them as non-negotiable attributes of the loan contract, presumably because borrowers underestimate their value, a case referred to as ``private paternalism'' by \cite{Laibson2018}. While \cite{Laibson2018} focuses on situations where the incentives of the firm align with those of the client, with overcollateralized loans, the lender may have incentives to \textit{encourage} default---using balloon payments or unstructured repayment loan contracts---in detriment of the borrower.

Do lenders have this incentive? Would structured payment features that commit borrowers to pay earlier lead to lower financial cost for borrowers?  Would borrowers freely demand such features? How can researchers rigorously estimate the benefits for borrowers who would freely choose the feature and for those that \textit{would not} choose it, necessary to assess paternalism? This paper answers these questions and studies the benefits of restricting borrower choice  in the context of one of the most prevalent and understudied forms of over-collateralized borrowing: pawn loans.

Pawn loans constitute one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}

In our context, assessing a case for paternalism involves rigorously evaluating whether imposing contract terms on a borrower can achieve lower financial cost than letting the borrower choose whether to have it. Often models (e.g. Roy models) \textit{assume} that agents self-select into contracts that are best for them. Using a novel one-stage three-armed randomized controlled experiment, including forced treatment and treatment choice arms, allow us to point identify the relevant TOT and TUT effects and \textit{test} that assumption in a real-world, high-stakes setting.\footnote{We can also estimate the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)---the average difference in untreated potential outcomes for those who choose commitment relative to those who do not, and the average selection on levels (ASL).}

%In some contexts the positive sorting assumption is compelling, it is not obvious in ours. Demand for commitment can be particularly low \citep{Ashraf,Gine, Royer,Ted,Sprenger}, and pawn-based borrowers are often financially illiterate.

%The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.  While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.  \cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.  Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies). In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT). This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.

%The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature. In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship. In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}. An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}.  A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}. This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice. Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions. Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.

Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing their pawn along with any payments made towards principal.  Indeed, 13\% of those who default first made some payments toward recovery, all of which is lost to them.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm. We use the labels commitment and structured payment contract interchangeably.

This design allows us to measure the effects of structured payments, and also the demand for this contractual feature. We demonstrate that it further allows us to estimate the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature. Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment. In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up. In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed. BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}. Two-stage Karlan-Zinman designs can be used to study a related question, namely isolating selection and incentive effects in comparing a more and less attractive intervention, such as low- and high-interest credit \citep{KarlanZinman2009} or cash grants versus loans \citep{Beaman2023}. Below we compare our novel one-stage design with these two-stage ones.

%We address three key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment? Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short. This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance. One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT). By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$. This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it. The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes. Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment. We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.

Turning to results, we find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees! Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' subjective values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments. Having said this, we don't have comprehensive measures of welfare and refrain from making welfare statements from the start. We focus exclusively on the cost of loan servicing, an important outcome.

On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not much discussed in the literature but that appears to be important in our context.

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from the structured payments contract. This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.

Next, we impose a two-sided exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the forcing-choice design point-identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.

In a one-shot interaction, the game between the borrower and the lender is zero-sum. Decreasing financial costs for the borrower means decreasing the lender's profit. However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender. A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by 11\%, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons. First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously. Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}

Our results raise two natural questions. First, in terms of regulatory policy, to what extent can we predict treatment effects and use those predictions to target frequent payment contracts? Second, why do borrowers seem to be leaving money on the table?

To address the first question, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. This requires that we impose the exclusion restriction not just on average, but at the level of individual borrowers, allowing us to make more precise personalized statements. Importantly, we estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured payment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in our context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates. From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is 92\%, while the actual average is only 44\%. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.

Our paper makes a number of contributions to the literature. First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for details.}  
we add to the relatively small literature that sheds light on private paternalism and selection on gains. In the context of food choice,  \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject. In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers. They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans. Our paper is complementary in several respects. Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.  \cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection. In contrast, we find no evidence of positive selection. Our design can be used in situations where compulsion of the treatment is possible but two-stage randomization is infeasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.}

%This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features.  This question is of interest in a large class of cases. Financial contracts frequently feature dimensions of private paternalism, such as mandatory frequent payment structures for loans. But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}. In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals. In the public policy domain we have seat belt mandates, age-dependent medical checkups, etc., which often go beyond nudging. Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.
%\footnote{The ``LATE-and-reweight'' approach goes beyond LATE by assuming no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate}. In our approach, we estimate selection-on-gains directly. Finally, as the MTE literature relies on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits}. In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE.}

%\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.

%\footnote{In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE % \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%. Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.}

>>>>

\title{Structured Payment in Pawnshop Borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

Pawnshop lending, where borrowers provide gold and other easily sold items to receive overcolleralized loans, are one of the most prevalent forms of credit in the world. loans are one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}. 
In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients. Compare this to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}. Pawn borrowers are not only numerous, they are also economically vulnerable. The vast majority of pawn loans are made to people with relatively low levels of education in times of significant stress.\footnote{A large literature shows stress impairs cognitive function, e.g. \cite{StressReview}.} Despite its prevalence and at-risk clientele, however, pawn lending has received little attention in the literature compared to other financial services.

Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits. At the same time, they frequently ``shroud'' these attributes by embedding them as non-negotiable features of the loan contract, presumably because borrowers undervalue commitment and would not demand it, given the choice. \cite{Laibson2018} refers to this practice as ``private paternalism''. When the incentives of firm and client align, as they do in \cite{Laibson2018}, private paternalism can benefit both parties. Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.\footnote{An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months. Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 15.8\% in interest if a loan is paid in full on the last day.}
Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts. Default is common.\footnote{The default rate in the \emph{status quo} arm of our Mexico City experiment is 44\%.}

This paper presents results from a randomized experiment that answers three key questions. First, does the absence of commitment-style contracts cause default in pawn lending? If so, to what extent does this benefit lenders? Second, if a commitment contract were available would pawn borrowers choose it? Even more importantly, would the \emph{right} borrowers choose it, i.e.\ those who would benefit the most? Third, is there a case for \emph{paternalism}, namely for mandating commitment in pawn lending? If so, should commitment be mandated for all borrowers or can it be effectively targeted? The question of choice versus paternalism is particularly salient in a setting with vulnerable borrowers. Yet comparing voluntary versus paternalistic policies is challenging. Even if commitment lowers financial costs on average, it may be ineffective or even harmful for borrowers who \emph{would not choose} to commit. To meet this challenge we introduce a novel three-armed design, the ``forcing-choice'' design, that allows us to shed light on these three questions in the important and under-studied context of pawn lending.

Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches. The control arm illustrates the costs of the \emph{status quo} contract: fully 44\% of control borrowers default, losing their pawn along with any payments made towards principal. Worse still, 29\% of those who default do so after making at least one payment towards recovery, a payment that they forfeit upon default. The ``forced commitment'' arm requires borrowers to make three monthly payments, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  Finally, the ``commitment choice'' arm offers borrowers the chance to opt in to the same structured monthly contract that is mandated for borrowers in the forced commitment arm.\footnote{When describing this new contract below, we use the terms ``commitment'' and ``structured payment'' interchangeably.}

Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment. The other two are a pair of randomized encouragement designs, each with one-sided non-compliance: one point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (treatment on the treated: TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (treatment on the untreated: TUT). 
Fully evaluating the case for paternalism versus borrower choice requires policymakers to learn not only whether those who demand commitment benefit from it (TOT), but also whether those who \emph{do not} are better off without it (TUT).

Our ATE results show that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average borrower in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates (APR), the financial cost of borrowing falls by 11 percentage points per loan (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees. The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it speed up payments, it also generates an early \emph{bifurcation} of borrowers into those that will recover their pawns and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. While we find that borrowers who experience structured payment contracts are 6 percentage points more likely borrow again from the same lender, a back-of-the-envelope calculation suggests that the commitment contract nevertheless lowers lender profits by \hl{11\% per borrower}. It is thus unsurprising that commitment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes. They approached us and requested help evaluating the causal effect of commitment.}

Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost. For example, our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value and to adjusting for lost liquidity from requiring monthly payments.

Despite the large financial cost savings of structured repayment, only 11\% of borrowers in the choice arm opt into the commitment contract. 
Could it be that borrowers who do not choose commitment are those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \emph{at least} 23\% of borrowers benefit from the structured payment contract. This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.

Next, we impose a pair of exclusion restrictions positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See\autoref{sec:testing_exclusion} \hl{for details--Frank will move some of this into the body of the text.}}
Under these restrictions, the forcing-choice design point-identifies the TOT and TUT, described above, along with the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, a measure of the empirical relevance of Roy-type selection.
Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had. 
Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a commitment contract, even when restricting attention to those who would not choose it voluntarily.

So why do borrowers seem to be leaving money on the table? 
While a simple measure of time inconsistency does not explain the large and positive TUT effect, we find that borrowers systematically overestimate the probability that they will recover their pawn: the average subjective probability of recovery is 92\% compared to a realized probability of 44\%.
Indeed, among borrowers who choose not to commit, we estimate the largest gains from commitment for those who overestimate their probability of recovery \emph{the most}.
This suggests that overconfidence may reduce the demand for commitment.

According to our conditional TUT results discussed above, mandating commitment contracts for all borrowers runs the risk of increasing financial costs for 7\% of the untreated. This raises the question of whether it is possible to assign commitment contracts in a \emph{targeted} way to only those borrowers who are likely to benefit from them. To answer this question, we revisit the causal forest results described above for the subset of borrowers who completed our baseline survey. Importantly, some variables from our survey that predict treatment effect heterogeneity cannot be used for targeting in practice. For example, while overconfident borrowers are more likely to default, targeting based on subjective probability of recovery may incentivize borrowers to change their reports, causing the predictive relationship to break down. Accordingly, our exercise restricts attention to survey variables that would be hard to manipulate (``narrow'' targeting). With this restriction, all of the targeting rules that we explore have relatively weak predictive power. Our best-performing targeting rule only lower the overall mis-targeting rate from 9.7\%--the baseline when all borrowers are assigned to commitment--to 9.5\%.

Our paper makes a number of contributions to the literature. First, we provide a detailed picture of pawn lending, a widespread and important financial service that, despite its prevalence and impact on economically vulnerable borrowers, has received little scholarly attention. While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the behavioral implications of such contracts remain largely unexplored. To our knowledge, ours is the first behavioral paper to focus on pawn lending specifically.

Second, we contribute to the relatively small literature on paternalism and selection-on-gains. In contrast to \cite{Laibson2018}, who studies private paternalism from a theoretical perspective, we show empirically that pawn borrowers would benefit, and lenders would suffer, from a paternalistic policy that mandates commitment in the form of structured repayment contracts. Unlike \cite{Sprenger}, who shows that individuals with the most time-inconsistent preferences are the least likely to demand commitment, we directly identify the treatment effect on the untreated (TUT). This obviates the need to first elicit preferences before testing for negative selection. Furthermore, whereas \cite{Walters} combines a distance-based instrument with structural modeling assumptions to show that students who select into more effective schools have smaller treatment effects ($\text{TOT} < \text{TUT}$), we identify the TUT and TOT effects without the need for a structural model. Instead, we rely on relatively weak exclusion restrictions whose testable implications we fail to reject.

Third, our paper makes a methodological contribution by introducing the ``forcing-choice'' design, a novel three-armed experiment that point identifies treatment effects for choosers (TOT) and non-choosers (TUT) under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of the causal parameters that are identified under this design, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for more details.}  
To our knowledge, this is the first paper to simultaneously point identify both quantities in the same experiment without the need for a structural model.\footnote{The forcing-choice design also point identifies the average selection-on-gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)--the difference in untreated potential outcomes for choosers versus non-choosers--and the average selection on levels (ASL)--the analogous comparison for treated potential outcomes. See Section \ref{sec:randchoice}.}
Our approach provides a valuable alternative to existing approaches for studying the relationship between treatment effects and treatment take-up. While the Marginal Treatment Effect (MTE) approach can be applied to either experimental or observational data provided that an instrumental variable is available, applying it requires additional modeling assumptions unless the instrument has a rich support set \citep{mogstad2018using}. The Becker-Degroot-Marschak (BDM) mechanism provides a theoretically attractive alternative that does not depend on structural modeling assumptions, but some recent studies have raised concerns about its reliability in practice \citep{bohm1997eliciting,banerji2014detection,mamadehussene2023reliability}.

The forcing-choice design differs from and complements other multi-armed designs from the literature.
As far as we are aware, our approach is the first to simultaneously identify both the TOT and TUT effects for within the same experiment, allowing us to study the empirical relevance of selection-on-gains.
The TUT effect, in particular, is crucial for considering the case for paternalism.
While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they instead identify \emph{two} TOT effects for different groups of ``treated'' households.
The well-known \cite{KarlanZinman2009} design, which randomly assigns interest rates in two stages to separate adverse selection from moral hazard, does not identify a TUT effect.
Like \cite{KarlanZinman2009}, \cite{Beaman2023} employ a two-stage randomization compared to the one-stage, three-armed approach in the forcing-choice design.
And while they identify a number of interesting causal parameters that shed light on the relationship between take-up and treatment effect heterogeneity, \cite{Beaman2023} do not identify a TUT effect or the average selection-on-gains.\footnote{In particular: the identify the ATE of cash grants, the TOT of loans, and the average effect of cash grants for those who would and would not accept a loan. While interesting, these last two effects are not TOT and TUT effects, because effects and compliance are defined with respect ti \emph{different} treatments: grants versus loans.}

Finally, we contribute to a growing literature on the effects of payment frequency in lending. Unlike previous experiments in microfinance markets \citep{Pande, barboni2023flexible, Field}, which find no benefits from regularized repayment environments, our experiment reveals significant positive effects in the context of pawn lending. The setting of these microfinance experiments differs from ours in an important way: they are performed on top of already highly structured microfinance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \citep{bauer2012behavioral}. This difference may explain why \cite{Pande} find almost no default in their control group, compared to 44\% in ours.
In addition to studying the effects of payment frequency, we examine both take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and would not choose it.

The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables. Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms. Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG and related causal effects under the forcing-choice design. Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
